Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-08 robdml.tex
app
tesx

Previous works suggest that an appropriate adversary for the inner
\emph{maximization} problem should increase the loss to an ``intermediate''
point between that of benign examples (\ie, unperturbed examples) and the
theoretical upper bound.
%
In this paper, we argue such point can be reached by a direct and efficient
adversary.
%
Besides, we conjecture the triplet sampling strategy has a key impact in
adversarial training, because it is also able to greatly influence the
mathematical expectation of loss even without adversarial attack.

@@

The use of existing assets, limitations and societal impact of our method
are discussed in supplementary material.

>>>>

Previous works imply that an appropriate adversary for the inner
\emph{maximization} problem should increase the loss to an ``intermediate''
point between that of benign examples (\ie, unperturbed examples) and the
theoretical upper bound.
%
In this paper, we argue such point can be reached by a direct and efficient
adversary.
%
Besides, we conjecture the triplet sampling strategy has a key impact in
adversarial training, because it is also able to greatly influence the
mathematical expectation of loss even without adversarial attack.

@@

Further technical details, discussions, limitations and societal impact of our
method are presented in supplementary.
